### 2014-06-22 dicook/map.Rmd
new explorations on school, age and gender

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(ggvis)
library(maps)
library(ggmap)
library(rworldmap)
library (grid)  	
library (scales)	
```

```{r load_data}
setwd("..")
sets <- c("item", "parent", "school", "scoredItem", "student")

@@

```{r modify_dictionaries}
# function to convert to data-frames
fn_make_df <- function(named_vector){
  data.frame(
    variable = attr(named_vector, "names"),
    description = named_vector,
    row.names = NULL
  )
}

@@

```{r usefulfn}
extractPolygons <- function(shapes) {

@@

```{r summarize}
sort(table(student2012$CNT))
schools.sampled <- summarise(group_by(student2012[,c(1,6)], CNT), numschools=length(unique(SCHOOLID)))
schools.sampled[order(schools.sampled$numschools, decreasing=T),]
```

```{r maps, fig.width=12, fig.height=7}
# Extract map polygons for modern world
world <- getMap(resolution = "low")
library(plyr)
world.polys <- extractPolygons(world)
detach("package:plyr")
# Subset data
student2012.sub <- student2012[, c(1:7, seq(501, 550, 5))]
colnames(student2012.sub)[1] <- "name"
student2012.sub$name <- as.character(student2012.sub$name)
# Check mismatches of names
# unique(anti_join(student2012.sub, world.polys)[1])
student2012.sub$name[student2012.sub$name=="Serbia"] <- "Republic of Serbia"
student2012.sub$name[student2012.sub$name=="Korea"] <- "South Korea"
student2012.sub$name[student2012.sub$name=="Chinese Taipei"] <- "Taiwan"
student2012.sub$name[student2012.sub$name=="Slovak Republic"] <- "Slovakia"
student2012.sub$name[student2012.sub$name=="Russian Federation"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Perm(Russian Federation)"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012.sub$name[student2012.sub$name=="China-Shanghai"] <- "China"
student2012.sub$name[student2012.sub$name=="China-Macau"] <- "China"
student2012.sub$name[student2012.sub$name=="Connecticut (USA)"] <- "United States of America"
student2012.sub$name[student2012.sub$name=="Florida (USA)"] <- "United States of America"
student2012.sub$name[student2012.sub$name=="Massachusetts (USA)"] <- "United States of America"

@@

```{r all, fig.width=8, fig.height=12}
student2012.sub.iqr <- summarise(group_by(student2012.sub[,c(1,8:17)], name), q0=min(PV1MATH, na.rm=T),
                                 q25=quantile(PV1MATH, 0.25, na.rm=T), q50=median(PV1MATH, na.rm=T), 
                                 q75=quantile(PV1MATH, 0.75, na.rm=T), q100=max(PV1MATH, na.rm=T), 
                                 count=length(PV1MATH))
student2012.sub.iqr$name <- factor(student2012.sub.iqr$name, 
      levels=student2012.sub.summary$name[order(student2012.sub.summary$math)])
ggplot(data=student2012.sub.iqr) + ylab("Math Score") + xlab("") + ylim(c(0,1000)) + 
  geom_point(aes(x=name, y=q50, size=count)) + geom_segment(aes(x=name, xend=name, y=q0, yend=q25)) +
  geom_segment(aes(x=name, xend=name, y=q75, yend=q100)) +
  coord_flip() + theme(legend.position="none")
student2012.sub.iqr <- summarise(group_by(student2012.sub[,c(1,8:17)], name), q0=min(PV1READ, na.rm=T),
                                 q25=quantile(PV1READ, 0.25, na.rm=T), q50=median(PV1READ, na.rm=T), 
                                 q75=quantile(PV1READ, 0.75, na.rm=T), q100=max(PV1READ, na.rm=T), 
                                 count=length(PV1READ))
student2012.sub.iqr$name <- factor(student2012.sub.iqr$name, 
      levels=student2012.sub.summary$name[order(student2012.sub.summary$read)])
ggplot(data=student2012.sub.iqr) + ylab("Reading Score") + xlab("") + ylim(c(0,1000)) + 
  geom_point(aes(x=name, y=q50, size=count)) + geom_segment(aes(x=name, xend=name, y=q0, yend=q25)) +
  geom_segment(aes(x=name, xend=name, y=q75, yend=q100)) +
  coord_flip() + theme(legend.position="none")
student2012.sub.iqr <- summarise(group_by(student2012.sub[,c(1,8:17)], name), q0=min(PV1SCIE, na.rm=T),
                                 q25=quantile(PV1SCIE, 0.25, na.rm=T), q50=median(PV1SCIE, na.rm=T), 
                                 q75=quantile(PV1SCIE, 0.75, na.rm=T), q100=max(PV1SCIE, na.rm=T), 
                                 count=length(PV1SCIE))
student2012.sub.iqr$name <- factor(student2012.sub.iqr$name, 
      levels=student2012.sub.summary$name[order(student2012.sub.summary$science)])
ggplot(data=student2012.sub.iqr) + ylab("Science Score") + xlab("") + ylim(c(0,1000)) + 
  geom_point(aes(x=name, y=q50, size=count)) + geom_segment(aes(x=name, xend=name, y=q0, yend=q25)) +
  geom_segment(aes(x=name, xend=name, y=q75, yend=q100)) +
  coord_flip() + theme(legend.position="none")
```

```{r pairs, fig.width=12, fig.height=12}
library(YaleToolkit)
gpairs(student2012.sub.summary[, c(2, 10, 11)])
# library(cranvas)
# qstudent <- qdata(student2012.sub.summary)
# qscatter(math, read, qstudent)
# qscatter(math, science, qstudent)
# qscatter(read, science, qstudent)
# record_selector(name, qstudent)
# Should do a PCA, to look at what countries do better on what types of math skills
student2012.sub.summary.nomiss <- subset(student2012.sub.summary, !is.na(student2012.sub.summary$Change)&!is.na(student2012.sub.summary$Employ))
rownames(student2012.sub.summary.nomiss) <- student2012.sub.summary.nomiss[,1]
student2012.sub.math.pca <- prcomp(student2012.sub.summary.nomiss[,2:9], scale=T, retx=T)
student2012.sub.math.pca
qplot(PC2, PC3, data=data.frame(student2012.sub.math.pca$x)) + theme(aspect.ratio=1)
# High values on PC2 correspond to high data and interpretation, low corresponds to high spatial 
# Ireland, UK, Greece, US states, Netherland, Norway, NZ, Finland, France, Croatia, Australia come up as high 
# on data and interp but less on spatial AND
# Chine, Albania, Taiwan, Kazakhstan, Korea, Japan, Russia come up as being high on spatial, less on data and interp
rownames(student2012.sub.math.pca$x)[order(student2012.sub.math.pca$x[,2], decreasing=T)]
# High on PC3 correspond to high quantification, employ, low on data
# Israel, Croatia, Estonia, Czech are high; Taiwan, Japan, Indonesia, Massachussetts, Jordan are low
rownames(student2012.sub.math.pca$x)[order(student2012.sub.math.pca$x[,3], decreasing=T)]
student2012.sub.summary.pca <- prcomp(student2012.sub.summary.nomiss[,c(2,10,11)], scale=T, retx=T)
student2012.sub.summary.pca
```

>>>>

```{r load_libraries, message=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(ggvis)
library(maps)
library(ggmap)
library(rworldmap)
library (grid)  	
library (scales)	
```

```{r load_data, echo=FALSE, warning=FALSE, message=FALSE}
setwd("..")
sets <- c("item", "parent", "school", "scoredItem", "student")

@@

```{r modify_dictionaries, echo=FALSE, warning=FALSE, message=FALSE}
# function to convert to data-frames
fn_make_df <- function(named_vector){
  data.frame(
    variable = attr(named_vector, "names"),
    description = named_vector,
    row.names = NULL
  )
}

@@

```{r usefulfn, echo=FALSE, warning=FALSE, message=FALSE}
extractPolygons <- function(shapes) {

@@

```{r summarize, warning=FALSE, message=FALSE}
sort(table(student2012$CNT))
schools.sampled <- summarise(group_by(student2012[,c(1,6)], CNT), numschools=length(unique(SCHOOLID)))
schools.sampled[order(schools.sampled$numschools, decreasing=T),]
```

```{r maps, fig.width=12, fig.height=7, warning=FALSE, message=FALSE}
# Extract map polygons for modern world
world <- getMap(resolution = "low")
library(plyr)
world.polys <- extractPolygons(world)
detach("package:plyr")
# Subset data
student2012.sub <- student2012[, c(1:7, seq(501, 550, 5))]
colnames(student2012.sub)[1] <- "name"
student2012.sub$name <- as.character(student2012.sub$name)
# Check mismatches of names
# unique(anti_join(student2012.sub, world.polys)[1])
student2012.sub$name[student2012.sub$name=="Serbia"] <- "Republic of Serbia"
student2012.sub$name[student2012.sub$name=="Korea"] <- "South Korea"
student2012.sub$name[student2012.sub$name=="Chinese Taipei"] <- "Taiwan"
student2012.sub$name[student2012.sub$name=="Slovak Republic"] <- "Slovakia"
student2012.sub$name[student2012.sub$name=="Russian Federation"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Perm(Russian Federation)"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012.sub$name[student2012.sub$name=="China-Shanghai"] <- "China"
student2012.sub$name[student2012.sub$name=="China-Macau"] <- "China"
student2012.sub$name[student2012.sub$name=="Connecticut (USA)"] <- "United States of America"
student2012.sub$name[student2012.sub$name=="Florida (USA)"] <- "United States of America"
student2012.sub$name[student2012.sub$name=="Massachusetts (USA)"] <- "United States of America"

@@

```{r all, fig.width=8, fig.height=12, warning=FALSE, message=FALSE}
student2012.sub.iqr <- summarise(group_by(student2012.sub[,c(1,8:17)], name), q0=min(PV1MATH, na.rm=T),
                                 q25=quantile(PV1MATH, 0.25, na.rm=T), q50=median(PV1MATH, na.rm=T), 
                                 q75=quantile(PV1MATH, 0.75, na.rm=T), q100=max(PV1MATH, na.rm=T), 
                                 count=length(PV1MATH))
student2012.sub.iqr$name <- factor(student2012.sub.iqr$name, 
      levels=student2012.sub.summary$name[order(student2012.sub.summary$math)])
ggplot(data=student2012.sub.iqr) + ylab("Math Score") + xlab("") + ylim(c(0,1000)) + 
  geom_point(aes(x=name, y=q50, size=count)) + geom_segment(aes(x=name, xend=name, y=q0, yend=q25)) +
  geom_segment(aes(x=name, xend=name, y=q75, yend=q100)) +
  coord_flip() + theme(legend.position="none")
student2012.sub.iqr <- summarise(group_by(student2012.sub[,c(1,8:17)], name), q0=min(PV1READ, na.rm=T),
                                 q25=quantile(PV1READ, 0.25, na.rm=T), q50=median(PV1READ, na.rm=T), 
                                 q75=quantile(PV1READ, 0.75, na.rm=T), q100=max(PV1READ, na.rm=T), 
                                 count=length(PV1READ))
student2012.sub.iqr$name <- factor(student2012.sub.iqr$name, 
      levels=student2012.sub.summary$name[order(student2012.sub.summary$read)])
ggplot(data=student2012.sub.iqr) + ylab("Reading Score") + xlab("") + ylim(c(0,1000)) + 
  geom_point(aes(x=name, y=q50, size=count)) + geom_segment(aes(x=name, xend=name, y=q0, yend=q25)) +
  geom_segment(aes(x=name, xend=name, y=q75, yend=q100)) +
  coord_flip() + theme(legend.position="none")
student2012.sub.iqr <- summarise(group_by(student2012.sub[,c(1,8:17)], name), q0=min(PV1SCIE, na.rm=T),
                                 q25=quantile(PV1SCIE, 0.25, na.rm=T), q50=median(PV1SCIE, na.rm=T), 
                                 q75=quantile(PV1SCIE, 0.75, na.rm=T), q100=max(PV1SCIE, na.rm=T), 
                                 count=length(PV1SCIE))
student2012.sub.iqr$name <- factor(student2012.sub.iqr$name, 
      levels=student2012.sub.summary$name[order(student2012.sub.summary$science)])
ggplot(data=student2012.sub.iqr) + ylab("Science Score") + xlab("") + ylim(c(0,1000)) + 
  geom_point(aes(x=name, y=q50, size=count)) + geom_segment(aes(x=name, xend=name, y=q0, yend=q25)) +
  geom_segment(aes(x=name, xend=name, y=q75, yend=q100)) +
  coord_flip() + theme(legend.position="none")
```

```{r oz, fig.width=8, fig.height=12, warning=FALSE, message=FALSE}
# Why is australia so varied?
student2012.sub.oz <- student2012.sub[student2012.sub$name=="Australia",]
student2012.sub.oz$SCHOOLID <- as.character(student2012.sub.oz$SCHOOLID)
#table(student2012.sub.oz$SCHOOLID)
#length(unique(student2012.sub.oz$SCHOOLID))
student2012.sub.oz.mean <- summarise(group_by(student2012.sub[,c(1,6, 8)], SCHOOLID), math=mean(PV1MATH, na.rm=T), 
                                     q0=min(PV1MATH, na.rm=T), q25=quantile(PV1MATH, p=0.25, na.rm=T), 
                                     q50=median(PV1MATH, na.rm=T),
                                     q75=quantile(PV1MATH, p=0.75, na.rm=T), q100=max(PV1MATH, na.rm=T))
student2012.sub.oz.mean$SCHOOLID <- factor(student2012.sub.oz.mean$SCHOOLID, levels=student2012.sub.oz.mean$SCHOOLID[order(student2012.sub.oz.mean$q50)])
ggplot(data=student2012.sub.oz.mean) + ylab("Math Score") + xlab("") + 
  geom_point(aes(x=SCHOOLID, y=q50)) + geom_segment(aes(x=SCHOOLID, xend=SCHOOLID, y=q0, yend=q25), alpha=0.1) +
  geom_segment(aes(x=SCHOOLID, xend=SCHOOLID, y=q75, yend=q100), alpha=0.1) +
  coord_flip() + theme(legend.position="none")
# So mostly the variation is student to student, not school to school like a friend suggested
# Not the best way to display this, I think
# Really want to be able to show that the best student at a low scoring school does better 
# than the worst student at a high-scoring school
```

```{r schoolmath, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
# Wonder how other countries compare
student2012.sub <- student2012[, c(1, 6, 501)]
colnames(student2012.sub)[1] <- "name"
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub.summary <- summarise(group_by(student2012.sub, name, SCHOOLID), math=median(PV1MATH, na.rm=T))
student2012.sub.summary$SCHOOLID <- as.numeric(as.character(student2012.sub.summary$SCHOOLID))
order <- summarise(group_by(student2012.sub, name, SCHOOLID), math=median(PV1MATH, na.rm=T))
bymedian <- with(student2012.sub.summary, reorder(name, math, median))
qplot(bymedian, math, data=student2012.sub.summary, ylim=c(0,1000), xlab="Math", ylab="") + coord_flip()
# Pretty similar overall, Australia still comes up as having a big variance, a few low-scoring schools 
# and a few high-scoring schools, Spain has a really low-scoring school
```

```{r pairs, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
library(YaleToolkit)
gpairs(student2012.sub.summary[, c(2, 10, 11)])
# library(cranvas)
# qstudent <- qdata(student2012.sub.summary)
# qscatter(math, read, qstudent)
# qscatter(math, science, qstudent)
# qscatter(read, science, qstudent)
# record_selector(name, qstudent)
# Should do a PCA, to look at what countries do better on what types of math skills
student2012.sub.summary.nomiss <- subset(student2012.sub.summary, !is.na(student2012.sub.summary$Change)&!is.na(student2012.sub.summary$Employ))
rownames(student2012.sub.summary.nomiss) <- student2012.sub.summary.nomiss[,1]
student2012.sub.math.pca <- prcomp(student2012.sub.summary.nomiss[,2:9], scale=T, retx=T)
student2012.sub.math.pca
qplot(PC2, PC3, data=data.frame(student2012.sub.math.pca$x)) + theme(aspect.ratio=1)
# High values on PC2 correspond to high data and interpretation, low corresponds to high spatial 
# Ireland, UK, Greece, US states, Netherland, Norway, NZ, Finland, France, Croatia, Australia come up as high 
# on data and interp but less on spatial AND
# Chine, Albania, Taiwan, Kazakhstan, Korea, Japan, Russia come up as being high on spatial, less on data and interp
rownames(student2012.sub.math.pca$x)[order(student2012.sub.math.pca$x[,2], decreasing=T)]
# High on PC3 correspond to high quantification, employ, low on data
# Israel, Croatia, Estonia, Czech are high; Taiwan, Japan, Indonesia, Massachussetts, Jordan are low
rownames(student2012.sub.math.pca$x)[order(student2012.sub.math.pca$x[,3], decreasing=T)]
student2012.sub.summary.pca <- prcomp(student2012.sub.summary.nomiss[,c(2,10,11)], scale=T, retx=T)
student2012.sub.summary.pca
```

### 2014-06-22 dicook/possessions.Rmd
new explorations on school, age and gender

```{r plotstuff2, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
student2012.sub.summary <- summarise(group_by(student2012.sub[,c(1,8,28,38)], name), 
              math05=mean(PV1MATH[numposs<6], na.rm=T), math06=mean(PV1MATH[numposs==6], na.rm=T), 
              math07=mean(PV1MATH[numposs==7], na.rm=T), math08=mean(PV1MATH[numposs==8], na.rm=T),
              math09=mean(PV1MATH[numposs==9], na.rm=T), math10=mean(PV1MATH[numposs==10], na.rm=T),
              math11=mean(PV1MATH[numposs==11], na.rm=T), math12=mean(PV1MATH[numposs==12], na.rm=T),
              math13=mean(PV1MATH[numposs==13], na.rm=T), math14=mean(PV1MATH[numposs==14], na.rm=T))
student2012.sub.summary.m <- melt(student2012.sub.summary)
student2012.sub.summary.m$variable <- substr(student2012.sub.summary.m$variable, 5, 6) 
student2012.sub.summary.m$variable <- as.numeric(student2012.sub.summary.m$variable)
qplot(variable, value, data=student2012.sub.summary.m, group=name, geom=c("point","smooth"), se=F) + 
  facet_wrap(~name, ncol=8)
```

@@

```{r agemath, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
student2012.sub <- student2012[, c(1, 14, 501)]
colnames(student2012.sub)[1] <- "name"
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$ST06Q01 <- as.numeric(student2012.sub$ST06Q01)
student2012.sub.summary <- summarise(group_by(student2012.sub, name), math=mean(PV1MATH, na.rm=T), 
          age=mean(ST06Q01, na.rm=T))
qplot(age, math, data=student2012.sub.summary)
# Age at start school does not seem to make a difference on country level
# qplot(ST06Q01, PV1MATH, data=student2012, alpha=I(0.1), xlab="Age", ylab="Math")
student2012.sub.summary <- summarise(group_by(student2012.sub, name), math4=mean(PV1MATH[ST06Q01==4], na.rm=T), 
          math5=mean(PV1MATH[ST06Q01==5], na.rm=T), math6=mean(PV1MATH[ST06Q01==6], na.rm=T), 
          math7=mean(PV1MATH[ST06Q01==7], na.rm=T), math8=mean(PV1MATH[ST06Q01>7], na.rm=T))
student2012.sub.summary.m <- melt(student2012.sub.summary)
student2012.sub.summary.m$variable <- substr(student2012.sub.summary.m$variable, 5, 5)
student2012.sub.summary.m$variable <- as.numeric(student2012.sub.summary.m$variable)
qplot(variable, value, data=student2012.sub.summary.m, group=name, geom=c("point","smooth"), se=F) + facet_wrap(~name, ncol=8)
# Looking by country is important: generally starting school early leads to better scores
```

>>>>

```{r plotstuff2, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
student2012.sub.summary <- summarise(group_by(student2012.sub[,c(1,8,28,38)], name), 
              math05=mean(PV1MATH[numposs<6], na.rm=T), math06=mean(PV1MATH[numposs==6], na.rm=T), 
              math07=mean(PV1MATH[numposs==7], na.rm=T), math08=mean(PV1MATH[numposs==8], na.rm=T),
              math09=mean(PV1MATH[numposs==9], na.rm=T), math10=mean(PV1MATH[numposs==10], na.rm=T),
              math11=mean(PV1MATH[numposs==11], na.rm=T), math12=mean(PV1MATH[numposs==12], na.rm=T),
              math13=mean(PV1MATH[numposs==13], na.rm=T), math14=mean(PV1MATH[numposs==14], na.rm=T))
student2012.sub.summary.m <- melt(student2012.sub.summary)
student2012.sub.summary.m$variable <- substr(student2012.sub.summary.m$variable, 5, 6) 
student2012.sub.summary.m$variable <- as.numeric(student2012.sub.summary.m$variable)
qplot(variable, value, data=student2012.sub.summary.m, group=name, geom=c("point","smooth"), se=F, 
      xlab="Possessions", ylab="Math") + 
  facet_wrap(~name, ncol=8)
```

@@

```{r agemath, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
student2012.sub <- student2012[, c(1, 14, 501)]
colnames(student2012.sub)[1] <- "name"
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$ST06Q01 <- as.numeric(student2012.sub$ST06Q01)
student2012.sub.summary <- summarise(group_by(student2012.sub, name), math=mean(PV1MATH, na.rm=T), 
          age=mean(ST06Q01, na.rm=T))
qplot(age, math, data=student2012.sub.summary)
# Age at start school does not seem to make a difference on country level
# qplot(ST06Q01, PV1MATH, data=student2012, alpha=I(0.1), xlab="Age", ylab="Math")
student2012.sub.summary <- summarise(group_by(student2012.sub, name), math4=mean(PV1MATH[ST06Q01==4], na.rm=T), 
          math5=mean(PV1MATH[ST06Q01==5], na.rm=T), math6=mean(PV1MATH[ST06Q01==6], na.rm=T), 
          math7=mean(PV1MATH[ST06Q01==7], na.rm=T), math8=mean(PV1MATH[ST06Q01>7], na.rm=T))
student2012.sub.summary.m <- melt(student2012.sub.summary)
student2012.sub.summary.m$variable <- substr(student2012.sub.summary.m$variable, 5, 5)
student2012.sub.summary.m$variable <- as.numeric(student2012.sub.summary.m$variable)
qplot(variable, value, data=student2012.sub.summary.m, group=name, geom=c("point","smooth"), se=F, 
      xlab="Age", ylab="Math") + 
  facet_wrap(~name, ncol=8)
# Looking by country is important: generally starting school early leads to better scores
```

```{r gendermath, fig.width=8, fig.height=12, warning=FALSE, message=FALSE}
student2012.sub <- student2012[, c(1, 12, 501)]
colnames(student2012.sub)[1] <- "name"
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub.summary <- summarise(group_by(student2012.sub, name), male=mean(PV1MATH[ST04Q01=="Male"], na.rm=T), 
          female=mean(PV1MATH[ST04Q01=="Female"], na.rm=T))
student2012.sub.summary.m <- melt(student2012.sub.summary)
colnames(student2012.sub.summary.m)[2] <- "gender"
colnames(student2012.sub.summary.m)[3] <- "math"
qplot(gender, math, data=student2012.sub.summary.m, geom="boxplot") + theme(aspect.ratio=1)
# Overall there is a gender gap in math, perhaps 10 points, and the high scores are almost exclusively males
student2012.sub.summary.m$name <- factor(student2012.sub.summary.m$name, 
      levels=student2012.sub.summary$name[order(student2012.sub.summary$male)])
student2012.sub.summary.m$gender <- factor(student2012.sub.summary.m$gender, levels=c("female", "male"))
qplot(name, math, data=student2012.sub.summary.m, colour=gender) + coord_flip()
# Some countries have no gender gap, a few surprises females better than males
student2012.sub.summary.gap <- summarise(group_by(student2012.sub.summary, name), gap=male-female)
student2012.sub.summary.gap$name <- factor(student2012.sub.summary.gap$name, 
      levels=student2012.sub.summary.gap$name[order(student2012.sub.summary.gap$gap)])
qplot(name, gap, data=student2012.sub.summary.gap, ylim=c(-30, 30)) + geom_hline(yintercept=0, colour="grey80") + coord_flip()
# Gap is interesting
```
